SAT Competition 2020\tnoteref{title}

### 2020-11-24 paper/main.tex
solver description

\paragraph{Kissat} 
three configurations submitted, four awards won, cdcl by several mixed strategies

\paragraph{CryptoMiniSat-CCAnr}
two variants: with and without lsids, with lsids slightly better, three awards won,  combination of cdcl and sls

\paragraph{Cadical Hack}
three configurations, two awards

\paragraph{MapleLCMDistCBT-DL Relaxed newTech}
this variant won two awards

\paragraph{MapleLCMDistCBT f2trc-s}
this variant won onw awards

\subsection{Incremental Library Track}
\paragraph{Cryptominisat-5}

@@

\paragraph{P-MCOMSPS-STR} three awards

\paragraph{Plingeling} three awards

\paragraph{ManyGlucose} two awards

\paragraph{Painless Maple} one award

@@

\paragraph{Mallob Mono}

\paragraph{TopoSAT 2}

\paragraph{Slime}

>>>>

\subsubsection{Kissat}

If it came to determine an overall winner of all the subtracks in the Main Track of this competition, then it would clearly be Kissat. 
Kissat was submitted in three configurations, including one default configuration and specialized configurations specifically tailored towards satisfiable or unsatisfiable instances, respectively.
Kissat won four awards, by achieving first place in the overall Main Track, first place in its Unsat Sub-Track, second place in the Sat Sub-Track and third place in the Planning Sub-Track.

Kissat is a reimplementation of Cadical~\cite{} in C, thus, taking advantage of finegrained control on the memory layout of new sophisticated data-structures used to manage watchers and clauses, e.g., through binary clause inlining, sentinel values and bit stuffing~\cite{}.

In Kissat forward subsumption for learned clauses was entirely replaced by more powerful vivification algorithms~\cite{}. 
For irredundant clauses forward subsumption is still executed together with variable eliminiation during pre- and inprocessing, but only in a very focused way, by carefully monitoring variable occurences~\cite{}.

Kissat also comes with a refined scheduling of inprocessing procedures based on growing conflict intervals. 
Regarding the duration of alternating restart modes, the Kissat authors considered conflict-rate being too unstable, and come up with ``ticks'', which is a new method to measure the length of two alternating restart-modes based on the approximate number of cache-line accesses.

Considering target phases~\cite{}, Kissat authors come up with an innovative use-case for autarkies to account for saved phases. 
Before each rephasing step they compute the largest autarky of the full assignment with an algorithm described in~\cite{}. 
The authors claim this autarky contains satisfying assignments of disconnected components which otherwise would get lost, and thus next, they are considered in variable elimination.

\subsubsection{CryptoMiniSat-CCAnr}

This solver won three awards, two third places in the Main Track and its Sat Subtrack, and one second place in the Planning Subtrack. 
It was submitted in two variants, with and without LSIDS~\cite{}, which is a phase selection heuristic similar to VSIDS and if active it is used only when backtracking is chronological. 
The version with LSIDS overall performed slightly better.

By tight integration of CCAnr, a stochastic local search (SLS) solver, into CryptoMinisat, CryptoMiniSat-CCAnr combines the two SAT solving strategies SLS and CDCL in a unique way. 
As in CaDiCal, they run local search for a short period of time in regular intervals and (just in case SLS finds no solution) change the polarities according to the best assignment found by the SLS solver~\cite{}.
In addition to this technique known as ``rephasing'' from CaDiCal, they bump VSIDS scores of the first 100 variables contained in the clauses which the SLS solver considers most hard to satisfy.

This version of CryptoMiniSat comes with an highly optimized implementation of Gauss-Jordan Elimination. 
CryptoMiniSat includes BreakId, a sub-system that calculates symmetry breaking clauses, which it calls on every 5th inprocessing iteration.

CryptoMiniSat changes decay factors of VSIDS and Maple heuristics dynamically after each inprocessing step to avoid sticking to a single best configuration.
As in CaDiCal (and now Kissat) CryptoMiniSat is switching between Polarity Caching and Stable Phases. \todo{It is not clear if this is also the case when LSIDS is activated.}
Inprocessing now also include ternary resolution.

\subsubsection{Cadical Hacks: Trail and AllUip}

This modified version of last years CaDiCal was submitted with the two new methods ``trail'' and ``alluip''. 
It was submitted in three configurations, one with both methods activated and two other with each having only one of them active. 
These hacks got two awards, second price in the Unsat Sub-Track of the Main Track and first price in the Planning Track.

\todo{describe trail and alluip hacks}

\subsubsection{MapleLCMDistCBT-DL Relaxed newTech}

The variant Relaxed-newTech of the MapleLCMDistCBT-DL solver won two awards, second price in Main Track and first price in its Sat Sub-Track.

\todo{}

\subsubsection{MapleLCMDistCBT f2trc-s}

The variant f2trc-s of the MapleLCMDistCBT solver was ranked third in the Unsat Sub-Track of the Main-Track.

\todo{}

\subsection{Incremental Library Track}
\subsubsection{Cryptominisat-5}
\todo{Merge with Main-Track winner description}

@@

\subsubsection{P-MCOMSPS-STR} three awards

\subsubsection{Plingeling} three awards

\subsubsection{ManyGlucose} two awards

\subsubsection{Painless Maple} one award

@@

\subsubsection{Mallob Mono}

\subsubsection{TopoSAT 2}

\subsubsection{Slime}
